|

### 2022-03-29 paper/paper.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE,
  warning = FALSE)
```

```{r libraries}
# Load libraries
library(tourr)
library(plotrix)
```

@@

```{r manualsequence, outwidth="80%", width=12, height=8, fig.cap="Sequence of projections where V3 contribution is changed."}
source("../code/manual.R")

# Base plot set up
plot.new()
par(pty="s", xaxt="n", yaxt="n", bty="n",
      omi=c(0,0,0,0), mar=c(0,0,0,0),
    mfrow=c(3,4))

# Create manual tour example
p <- 4
d <- 2
set.seed(24)
A <- matrix(runif(p*d, min=-1), ncol=d, byrow=TRUE)
colnames(A) <- c("P1", "P2")
rownames(A) <- paste0("V", 1:p)
A <- tourr::orthonormalise(A)
plot_basis(A)

# Now set a new position
vchange <- 3
eps <- 0.02

# Iterate and save images
for (i in 1:11) {
  flname <- paste0("mtour_plots/mtour", i, ".png")
  A[vchange,] <- A[vchange,]*(1-i*eps)
  A <- tourr::orthonormalise(A)
  #png(flname, width=250, height=250)
  plot_basis(A)
  #dev.off()
}
```
